---
title: "Conjoint Analysis Team Project"
output: html_document

date: "2025-06-20"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
```

## Purpose and product
The following is a conjoint analysis for a breakfast product to be sold in Tokyo , mainly targetting office professionals.

## Defining the attributes

The research will include six attributes.
Conventional attributes: 
* Price
* Form
* Purchase Location

Innovative attributes:
* Fun Packaging
* Cognitive Support
* Digital Integration 


Loading the data and creating the attribute: 

```{r, echo = FALSE}
# load required libraries
library(conjoint)
library(dplyr)
library(purrr)
library(readxl)
library(usethis)
library(ggplot2)
library(knitr)

# source custom functions from Shingo-sensei
source("SCRIPTS/conjoint_tool_new.R")

# define the attributes
attribute <- list(
  Price = c("200", "400", "600"),
  Form = c("Bread and Pastries","Wrap","Yougurt Jelly"),
  PurchaseLocation = c("On Route to work","Within 150m", "More than 150m"),
  FunPackaging = c("None", "Attack on Titan", "Doan Ritsu"),
  CognitiveSupport = c("None","Caffeine or Alertness boost",
                       "Natural Mood Stabilizer"),
  DigitalIntegration = c("None", "Loyalty points", "Nutrition Advice")
)

kable(data.frame(attribute))
```

## Generating products for survey

To generate the combinations for the survey, we run:

```{r}
# Step 2: Profile Construction
# Full factorial design
profiles <- expand.grid(attribute)

# Orthogonal design
design.o <- caFactorialDesign(data=profiles, type="fractional", cards=13)


kable(design.o)
```


